Exploring the Shadows of Terror: The Influence of Terrorism on Public Opinion and Democratic Values

### 2024-02-15 outputs/paper/paper.qmd

@@

The paper is structured as follows: it begins with an overview of the methodological framework guiding our analysis in the Data section, followed by a presentation of our findings in the Results section. We then discuss these findings in the context of their broader implications for democracy and conclude with recommendations for future research and policy considerations in the Discussion section.

>>>>

The paper delves into the complex dynamics of terrorism's influence on public political opinion. It extends the discourse beyond conventional analysis to explore how various expressions of terrorism—from domestic to international incidents—affect public attitudes, with a particular focus on outgroup hostility, political conservatism, and rally-'round-the-flag phenomena. Despite a growing body of research in this field, a significant gap persists in understanding the holistic and nuanced effects of different forms of terrorism across diverse sociopolitical contexts. To address this gap, we systematically analyze and integrate findings from prior research, employing a variety of methodological approaches to offer a comprehensive overview of terrorism's impact on public sentiment.

@@
